---
title: "flat_preprocess_2019_health.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r setup}
library(here)
library(targets)
tar_load(dharma2019, store = here::here("_targets"))

# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)

library(janitor)
library(dplyr)
library(tidyr)
library(lubridate)
library(skimr)
library(forcats)
library(stringr)
library(ggplot2)
```

This notebooks deals with the 2019 file's health data.

Let's begin:

## Level 1 Health Data

The data is organized into 2 levels, where level 1 is the individual
baseline data, and level 2 is the follow up data.

### Reading in the data

The data is read in from the targets pipeline, and is contained in the `dharma2019` object.

To get the same number of rows we rerun the same NA filtering as
in the cohort 2019 notebook:

```{r}
cohort_df <- dharma2019$`Level 1 Named`

# create household head name
household_df <- dharma2019$`Level 0 Named` %>%
  select(fact_0_id, L0_q2_hh_name) %>%
  rename(hh_head_name = L0_q2_hh_name) %>%
  distinct() %>%
  mutate(hh_head_name = na_if(hh_head_name,".")) %>%
  filter(!is.na(hh_head_name))

# some na filtering
cohort_df %>%
  fill(fact_0_id, .direction = "down") %>%
  filter(!is.na(L1_q39_date)) %>%
  filter(L1_q39_date != ".") %>% 
  filter(!is.na(L1_q1_name)) %>%
  filter(L1_q1_name != ".") %>% 
  filter(!is.na(L1_q1_name)) %>%
  filter(L1_q1_name != ".") %>% 
  filter(!is.na(L1_q8_gender)) %>%
  filter(L1_q8_gender != ".") %>%
  filter(!is.na(L1_q2_dob_year)) %>%
  filter(L1_q2_dob_year != ".") %>%

  #join household head name
  left_join(household_df, by = "fact_0_id") -> cohort_2019_health
```

We can use the data dictionary to see what columns are available.

```{r}
dharma2019_dict <- dharma2019$`Data Dictionary`
dharma2019_dict %>%
  fill(level, .direction = "down") -> dharma2019_dict

level_1_dict <- dharma2019_dict %>%
  filter(level == 1)
level_1_dict

level_1_dict <- dharma2019_dict %>%
  filter(level == 1)
level_1_dict
```

Now, to get the matching health columns for 2019, we match the
2018 health columns to the most relevant 2019 columns.

### Health Care Access & Diagnoses

This section will align with the `prior_health_care` and `prior_diagnoses` sections

```{r}
cohort_2019_health %>%
  select(L1_q16_visit_hosp_clinic) %>%
  table()
```

```{r}
cohort_2019_health %>%
  mutate(prior_health_care_clean = case_when(
    L1_q16_visit_hosp_clinic == "Yes" ~ "Yes",
    L1_q16_visit_hosp_clinic == "No" ~ "No",
    L1_q16_visit_hosp_clinic == "IDK" ~ "Unknown",
    TRUE ~ NA_character_
  ) %>% as.factor()) -> cohort_2019_health_
```

We fortunately already have the diagnoses in wide format so we can work with that:

```{r}
diagnoses <- level_1_dict %>%
  fill(column_name, .direction = "down") %>%
  filter(str_detect(column_name, "q17_diagnostic")) %>%
  select(choice_name) %>%
  pull(choice_name) %>%
  make_clean_names() %>%
  str_replace_all("vih", "hiv") %>%
  str_c("diag_", ., "_clean")

```

Now, we can rename the columns in the health table with these
diagnoses:
```{r}
ind_diagnoses <- names(cohort_2019_health_) %>%
  str_detect("L1_q17_diagnostic") %>%
  which()

names(cohort_2019_health_)[ind_diagnoses] <- diagnoses
```

```{r}
# cohort_2019_health_ %>%
#   mutate(across(contains("diag_"), ~ case_when(
#     . == "." ~ NA,
#     . == NA ~ NA
#   ) %>% as.factor())) -> cohort_2019_health_
  
cohort_2019_health_%>%
  select(contains("diag_")) %>%
  glimpse()
```

Much easier! Now, we deal with the "other" diagnoses:

```{r}
cohort_2019_health_ %>%
  tabyl(L1_q18_other_diagnostic)
```

This will require some manual cleaning as well as the same strategy for
cleaning the "other" diagnoses as we did in the 2018 notebook, using a
translation lookup table.

We'll leave this for now.

### Vaccinations

Categorising vaccinations will be similar to 2018:

```{r}
cohort_2019_health_ %>%
  select(L1_q26_vaccine_card) %>%
  table()
```

## Level 2 Health Data

In addition to this, there are level 2 health data that is collected
for each individual multiple times per year. These are called `followups`.

```{r}
cohort_2019_anthro <- dharma2019$`Level 2 Named`
level_2_dict <- dharma2019_dict %>%
  filter(level == 2)
```

The level 2 data is collected at the following time points:

```{r}
cohort_2019_anthro %>%
  select(L2_q38_date_followup) %>%
  mutate(date = L2_q38_date_followup %>%
    na_if("\\.") %>% 
    as.numeric() %>%
    convert_to_date()) %>%
  select(date) %>%
  ggplot(aes(x = date)) +
  geom_histogram(binwidth = 30) +
  labs(title = "Level 2 data collection dates in 2019", x = "Date", y = "Count")
```

As we can see, the data is supposed to correspond to a 2019 data collection
window, but extends to almost the end of 2020.

Naively, we can check to see if people get multiple surveys:

```{r}
cohort_2019_anthro %>%
  fill(fact_1_id, .direction = "down") %>%
  filter(!deleted) %>%
  group_by(fact_1_id) %>%
  summarise(n_surveys = n()) %>%
  arrange(-n_surveys)
```

It seems that an individual could have 20 entries in one
file:

```{r}
cohort_2019_anthro %>%
  fill(fact_0_id, fact_1_id, .direction = "down") %>%
  filter(!deleted) %>%
  filter(fact_1_id == 8864710) %>%
  mutate(date = L2_q38_date_followup %>%
    na_if("\\.") %>% 
    as.numeric() %>%
    convert_to_date()) %>%
  select(date) %>% table()
```

Ok, it is encouraging that the dates are all different. This would mean that,
for some people, they have multiple follow ups in the same year.

Let's see how many follows ups the average person has:

```{r}
cohort_2019_anthro %>%
  fill(fact_0_id, fact_1_id, .direction = "down") %>%
  filter(!deleted)
```

Ok, with that known, we can preprocess these anthro entries. We know
that each individual can have multiple entries, so we need to remove the deleted entries
and then order each individual by date to know which follow up is which:

```{r}
cohort_2019_anthro %>%
  fill(fact_0_id, fact_1_id, .direction = "down") %>%
  filter(!deleted) %>%
  filter(L2_q38_date_followup != ".") %>%
  mutate(date_clean = L2_q38_date_followup %>%
    na_if("\\.") %>% 
    as.numeric() %>%
    convert_to_date()) -> cohort_2019_anthro_
```

### Demographics

First, we look at the demographics within follow ups.

The status of the individual is first:

```{r}
cohort_2019_anthro_ %>%
  select(fact_1_id, L2_q41_alive) %>%
  tabyl(L2_q41_alive)
```

```{r}
cohort_2019_anthro_ %>%
  tabyl(L2_q47_participate)
```

```{r}
cohort_2019_anthro_ %>%
  tabyl(L2_q46_present)
```

This filters out the individuals who are not alive, not participating, or not present.

```{r}
cohort_2019_anthro_ %>%
  filter(L2_q47_participate == "Yes") %>%
  filter(L2_q41_alive == "Yes") %>%
  filter(L2_q46_present == "Yes") -> cohort_2019_anthro_
```

### Maternal Health

Now we look at recent pregnancies:

```{r}
cohort_2019_anthro_ %>%
  select(fact_1_id, L2_q196_live_birth) %>%
  tabyl(L2_q196_live_birth)
```

60 individuals is enough to keep around:

```{r}
cohort_2019_anthro_ %>%
  mutate(recent_birth_clean = case_when(
    L2_q196_live_birth == "Yes" ~ TRUE,
    L2_q196_live_birth == "No" ~ FALSE,
    L2_q196_live_birth == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) -> cohort_2019_anthro_
```

If they are currently pregnant:

```{r}
cohort_2019_anthro_ %>%
  select(fact_1_id, L2_q200_pregnant_now) %>%
  tabyl(L2_q200_pregnant_now)
```

That's a large number of individuals who are pregnant, so we can keep this
column as well:

```{r}
cohort_2019_anthro_ %>%
  mutate(pregnant_now_clean = case_when(
    L2_q200_pregnant_now == "Yes" ~ TRUE,
    L2_q200_pregnant_now == "No" ~ FALSE,
    L2_q200_pregnant_now == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) -> cohort_2019_anthro_
```

The other pregnancy columns do not seem to be relevant for analysis, but we
may include them later.

### Diagnoses

Recent diagnoses are collected here as well. We're going to use the
lookup table from the 2018 data to rename the columns:

```{r}
diagnoses <- level_2_dict %>%
  fill(column_name, .direction = "down") %>%
  filter(str_detect(column_name, "q62_diagnostic")) %>%
  mutate(raw = make_clean_names(choice_name)) %>%
  select(raw) %>%
  left_join(malagasy_diagnosis_lookup_table) %>%
  pull(diagnosis_english) %>%
  str_c("diag_", ., "_clean")

ind_diagnoses <- names(cohort_2019_anthro_) %>%
  str_detect("q62_diagnostic") %>%
  which()

names(cohort_2019_anthro_)[ind_diagnoses] <- diagnoses
```

Here's a specific diagnosis we want to single out: Malaria (called RDT in Malagasy):

```{r}
cohort_2019_anthro_ %>%
  select(L2_q226_rdt_test, L2_q227_rdt_result) %>%
  table()
```

We can replace whenever we have malaria diagnosis with
the results of the RDT test:

```{r}
cohort_2019_anthro_ %>%
  mutate(diag_malaria_rdt_positive_clean = case_when(
    diag_malaria_rdt_positive_clean == TRUE ~ TRUE,
    L2_q227_rdt_result == "Positive" ~ TRUE,
    L2_q227_rdt_result == "Negative" ~ FALSE,
    TRUE ~ NA
  ) %>% as.factor()) -> cohort_2019_anthro_
```

### Symptoms

We can process the set of specific symptoms next:

```{r}
cohort_2019_anthro_ %>%

  #diarrhea
  mutate(symptom15dys_diarrhea_clean = case_when(
    L2_q94_diarrhea_now_15days == "Yes" ~ TRUE,
    L2_q94_diarrhea_now_15days == "No" ~ FALSE,
    L2_q94_diarrhea_now_15days == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) %>%

  #fever
  mutate(symptom15dys_fever_clean = case_when(
    L2_q117_fever_now_15days == "Yes" ~ TRUE,
    L2_q117_fever_now_15days == "No" ~ FALSE,
    L2_q117_fever_now_15days == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) %>%

  # emesis
  mutate(symptom15dys_vomit_clean = case_when(
    L2_q137_vomit_now_15days == "Yes" ~ TRUE,
    L2_q137_vomit_now_15days == "No" ~ FALSE,
    L2_q137_vomit_now_15days == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) %>%

  # headache
  mutate(symptom15dys_headache_clean = case_when(
    L2_q236_headache_15days == "Yes" ~ TRUE,
    L2_q236_headache_15days == "No" ~ FALSE,
    L2_q236_headache_15days == "." ~ NA,
    TRUE ~ NA
  ) %>% as.factor()) -> cohort_2019_anthro_
```

## Structure

We will add a function to show us what the time frame
of a specific person's follow up is:

```{r}
cohort_2019_anthro_ %>%
  mutate(uuid_clean = fact_1_id) %>%
  group_by(uuid_clean) %>%
  arrange(uuid_clean, date_clean) %>%
  mutate(followup_number_clean = row_number()) %>%
  ungroup() %>%
  mutate(across(contains("diag_"), ~ case_when(
    . == "." ~ NA,
    is.na(.) ~ NA,
    TRUE ~ TRUE
  ) %>% as.factor())) %>%
  rename(village_clean = L2_q791_enumerator) %>%
  select(contains('clean')) %>%
  select(-contains("L2")) %>%
  select(uuid_clean, followup_number_clean, date_clean, village_clean, everything()) -> x

skimr::skim(x)

```

# preprocess_rdp_health_subset2019

This function will preprocess a subset of the RDP health data for 2019.
  
```{r function-preprocess_rdp_health_subset}
#' RDP Health Subset Preprocessing
#' 
#' This function preprocesses the 2019 data to extract a subset of health-related information.
#' It focuses on cleaning and organizing health data for the RDP paper.
#' 
#' @return
#' 
#' @export
preprocess_rdp_health_subset2019 <- function(dharma2019){
    
    cohort_2019_anthro <- dharma2019$`Level 2 Named`
    dharma2019_dict <- dharma2019$`Data Dictionary`
    dharma2019_dict %>%
      fill(column_name, level, .direction = "down") %>%
      fill(level, .direction = "down")  -> dharma2019_dict
    level_2_dict <- dharma2019_dict %>%
      filter(level == 2)

    cohort_2019_anthro %>% 
      fill(fact_0_id, fact_1_id, .direction = "down") %>%
      filter(!deleted) %>%
      filter(L2_q38_date_followup != ".") %>%
      mutate(date_clean = L2_q38_date_followup %>%
        na_if("\\.") %>% 
        as.numeric() %>%
        convert_to_date()) -> cohort_2019_anthro_

    cohort_2019_anthro_ %>%
      filter(L2_q47_participate == "Yes") %>%
      filter(L2_q41_alive == "Yes") %>%
      filter(L2_q46_present == "Yes") -> cohort_2019_anthro_
    
    cohort_2019_anthro_ %>%
      mutate(recent_birth_clean = case_when(
        L2_q196_live_birth == "Yes" ~ TRUE,
        L2_q196_live_birth == "No" ~ FALSE,
        L2_q196_live_birth == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2019_anthro_

    cohort_2019_anthro_ %>%
      mutate(pregnant_now_clean = case_when(
        L2_q200_pregnant_now == "Yes" ~ TRUE,
        L2_q200_pregnant_now == "No" ~ FALSE,
        L2_q200_pregnant_now == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2019_anthro_

    diagnoses <- level_2_dict %>%
      
      filter(str_detect(column_name, "q62_diagnostic")) %>%
      mutate(raw = make_clean_names(choice_name)) %>%
      select(raw) %>%
      left_join(malagasy_diagnosis_lookup_table) %>%
      pull(diagnosis_english) %>%
      str_c("diag_", ., "_clean")

    ind_diagnoses <- names(cohort_2019_anthro_) %>%
      str_detect("q62_diagnostic") %>%
      which()

    names(cohort_2019_anthro_)[ind_diagnoses] <- diagnoses

    cohort_2019_anthro_ %>%

      # malaria
      mutate(diag_malaria_rdt_positive_clean = case_when(
        diag_malaria_rdt_positive_clean == TRUE ~ TRUE,
        L2_q227_rdt_result == "Positive" ~ TRUE,
        L2_q227_rdt_result == "Negative" ~ FALSE,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      #diarrhea
      mutate(symptom15dys_diarrhea_clean = case_when(
        L2_q94_diarrhea_now_15days == "Yes" ~ TRUE,
        L2_q94_diarrhea_now_15days == "No" ~ FALSE,
        L2_q94_diarrhea_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      #fever
      mutate(symptom15dys_fever_clean = case_when(
        L2_q117_fever_now_15days == "Yes" ~ TRUE,
        L2_q117_fever_now_15days == "No" ~ FALSE,
        L2_q117_fever_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      # emesis
      mutate(symptom15dys_vomit_clean = case_when(
        L2_q137_vomit_now_15days == "Yes" ~ TRUE,
        L2_q137_vomit_now_15days == "No" ~ FALSE,
        L2_q137_vomit_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      # headache
      mutate(symptom15dys_headache_clean = case_when(
        L2_q236_headache_15days == "Yes" ~ TRUE,
        L2_q236_headache_15days == "No" ~ FALSE,
        L2_q236_headache_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2019_anthro_
      
    cohort_2019_anthro_ %>%
      mutate(uuid_clean = as.character(fact_1_id)) %>%
      group_by(uuid_clean) %>%
      arrange(uuid_clean, date_clean) %>%
      mutate(followup_number_clean = row_number()) %>%
      ungroup() %>%
      mutate(across(contains("diag_"), ~ case_when(
        . == "." ~ NA,
        is.na(.) ~ NA,
        TRUE ~ TRUE
      ) %>% as.factor())) %>%
      rename(village_clean = L2_q791_enumerator) %>%
      select(contains('clean')) %>%
      select(-contains("L2")) %>%
      select(uuid_clean, followup_number_clean, date_clean, village_clean, everything())
}
```

  
```{r tests-preprocess_rdp_health_subset}
test_that("preprocess_rdp_health_subset works", {
  expect_true(inherits(preprocess_rdp_health_subset2019, "function")) 
})
```

# preprocess_rdp_health_subset2020

Similar to above, we can define a function to preprocess the 2020 health followups.
  
It looks like the 2020 data has a similar structure to the 2019 data, so we can
use a similar approach. Confusingly, it uses `L0` as the prefix, which has
usually been reserved for household-level data. However, we can see in the `names`
that `fact_1_id` is the individual identifier, and the date column is `L0_q38_date_followup`.

So this must be a follow up file.

```{r}
tar_load(dharma2020, store = here::here("_targets"))
```

```{r}
cohort_2020_anthro <- dharma2020
names(cohort_2020_anthro) %>%
  str_subset("date") %>%
  sort()
```

So what we need to find are the same health columns from 2019, but in 2020. Do the
same number of surveys per person exist?:

```{r}
cohort_2020_anthro %>%
  filter(!deleted) %>%
  filter(L0_q856_unique_id_if_unable_to_select_from_dropdown_above != ".") %>%
  group_by(L0_q856_unique_id_if_unable_to_select_from_dropdown_above) %>%
  summarise(n_surveys = n()) %>%
  arrange(-n_surveys)
```

It looks like each person has only one followup survey, but there are some with 6.

We need to be sure we are selecting the right identifier. Let's look at the columns with
a valid name, and the column where they select a name from the drop down:

Individuals with a name and ID number:

```{r}
cohort_2020_anthro %>%
  select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above) %>%
  # remove rows where there is neither a name or id
  filter(name != "." & id != ".") %>%
  group_by(name, id) %>%
  summarise(n = n()) %>%
  arrange(-n) %>% summary()
```

Over 800 cases, the vast majority of whom have only 1 count.

Individuals with a name but no ID:

```{r}
cohort_2020_anthro %>%
  select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above) %>%
  # remove rows where there is a name but no id
  filter(name != "." & id == ".") %>%
  group_by(name, id) %>%
  summarise(n = n()) %>%
  arrange(-n) %>% summary()
```

Over 1830 cases, and the vast majority have over 14 entries. This is the
group we should be using as the "correct" data.

Individuals with no name but an ID:

```{r}
cohort_2020_anthro %>%
  select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above,) %>%
  # remove rows where there is no name but there is an id
  filter(name == "." & id != ".") %>%
  group_by(name, id) %>%
  summarise(n = n()) %>%
  arrange(-n) %>% summary()
```

1900 cases, with the median number of entries as 2.

If someone has no name but does have an ID, can we find them in the set that has both a name and an ID?

```{r}
cohort_2020_anthro %>%
  select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above) %>%
  # remove rows where there is no name but there is an id
  filter(name == "." & id != ".") %>%
  left_join(
    cohort_2020_anthro %>%
      select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above,) %>%
      # remove rows where there is neither a name or id
      filter(name != "." & id != ".") %>%
      distinct(),
    by = "id"
  ) %>%
  filter(!is.na(name.y)) %>%
  group_by(name.x, id, name.y) %>%
  summarise(n = n()) %>%
  arrange(-n)
```

These 8 IDs appear twice — first they have an ID but no name, and in another
follow up they have both an ID and a name. This means that it is extremely
rare that someone has a follow up where they did not select the right name.

This means that people who have a name and an ID are the most reliable, and
people with a name and no ID are the next most reliable. People with
no name but an ID are the least reliable, and should likely be removed.
How much data would we lose?

```{r}
cohort_2020_anthro %>%
  select(name = L0_q813_who_are_you_following_up_with_individual_id, id = L0_q856_unique_id_if_unable_to_select_from_dropdown_above,) %>%
  # remove rows where there is no name but there is an id
  filter(name == "." & id != ".") -> no_name

nrow(no_name) / nrow(cohort_2020_anthro)
```

About 10%, this is acceptable.

Below we confirm that this dataset continues the follow ups from 2021 (the end of our 2019 dataset) onwards:

```{r}
cohort_2020_anthro %>%
  select(L0_q38_date_followup) %>%
  mutate(date = L0_q38_date_followup %>%
    na_if("\\.") %>% 
    # as.numeric() %>%
    dmy_hms()) %>%
  select(date) %>%
  ggplot(aes(x = date)) +
  geom_histogram() +
  labs(title = "Level 0 data collection dates in 2020", x = "Date", y = "Count")
```

Ok, so now we know the basic first filters: we remove deleted entries, as well
as entries with no name. Then we'll additionally create a unique ID
for each individual by combining the name and ID columns.

```{r}
cohort_2020_anthro %>%
  filter(!deleted) %>%
  filter(L0_q813_who_are_you_following_up_with_individual_id != ".") %>%
  filter(L0_q38_date_followup != ".") %>%
  mutate(uuid_clean = str_c(
    L0_q813_who_are_you_following_up_with_individual_id, 
    L0_q856_unique_id_if_unable_to_select_from_dropdown_above, 
    sep = "_")) %>%
  filter(uuid_clean != "._") %>%
  rowwise() %>%
  mutate(uuid_clean = generate_uid(salt=Sys.getenv("UUID_SALT"), uuid_clean)) %>%
  ungroup() -> cohort_2020_anthro_
```

With that done, we can now select the same health columns as in 2019.

```{r}
names(cohort_2019_anthro_) %>% str_remove("L2_") -> names_2019
names(cohort_2020_anthro_) %>% str_remove("L0_") -> names_2020

names_2020[names_2020 %in% names_2019]
```

```{r development-preprocess_rdp_health_subset2020}
# You can prepare the code of the preprocess_rdp_health_subset2020() function here
```


```{r function-preprocess_rdp_health_subset2020}
#' Title
#' 
#' Description
#' 
#' @return
#' 
#' @export
preprocess_rdp_health_subset2020 <- function(dharma2020, dharma2019_dict){
    
    cohort_2020_anthro <- dharma2020
    
    dharma2019_dict %>%
      fill(column_name, level, .direction = "down") %>%
      fill(level, .direction = "down")  -> dharma2019_dict
    level_2_dict <- dharma2019_dict %>%
      filter(level == 2)

    cohort_2020_anthro %>% 
      # fill(fact_0_id, fact_1_id, .direction = "down") %>%
      filter(!deleted) %>%
      filter(L0_q38_date_followup != ".") %>%
      mutate(date_clean = L0_q38_date_followup %>%
        na_if("\\.") %>% 
        dmy_hms()) -> cohort_2020_anthro_

    cohort_2020_anthro_ %>%
      filter(L0_q47_participate == "Yes") %>%
      filter(L0_q41_alive == "Yes") %>%
      filter(L0_q46_present == "Yes") -> cohort_2020_anthro_
    
    cohort_2020_anthro_ %>%
      mutate(recent_birth_clean = case_when(
        L0_q196_live_birth == "Yes" ~ TRUE,
        L0_q196_live_birth == "No" ~ FALSE,
        L0_q196_live_birth == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2020_anthro_

    cohort_2020_anthro_ %>%
      mutate(pregnant_now_clean = case_when(
        L0_q200_pregnant_now == "Yes" ~ TRUE,
        L0_q200_pregnant_now == "No" ~ FALSE,
        L0_q200_pregnant_now == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2020_anthro_

    diagnoses <- level_2_dict %>%
      
      filter(str_detect(column_name, "q62_diagnostic")) %>%
      mutate(raw = make_clean_names(choice_name)) %>%
      select(raw) %>%
      left_join(malagasy_diagnosis_lookup_table) %>%
      pull(diagnosis_english) %>%
      str_c("diag_", ., "_clean")

    ind_diagnoses <- names(cohort_2020_anthro_) %>%
      str_detect("q62_diagnostic") %>%
      which()

    if(length(ind_diagnoses) != length(diagnoses)){
      stop("number of diagnoses does not match number of diagnosis columns in 2020 data")
    }

    names(cohort_2020_anthro_)[ind_diagnoses] <- diagnoses

    cohort_2020_anthro_ %>%

      # malaria
      mutate(diag_malaria_rdt_positive_clean = case_when(
        diag_malaria_rdt_positive_clean == TRUE ~ TRUE,
        L0_q227_rdt_result == "Positive" ~ TRUE,
        L0_q227_rdt_result == "Negative" ~ FALSE,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      #diarrhea
      mutate(symptom15dys_diarrhea_clean = case_when(
        L0_q94_diarrhea_now_15days == "Yes" ~ TRUE,
        L0_q94_diarrhea_now_15days == "No" ~ FALSE,
        L0_q94_diarrhea_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      #fever
      mutate(symptom15dys_fever_clean = case_when(
        L0_q117_fever_now_15days == "Yes" ~ TRUE,
        L0_q117_fever_now_15days == "No" ~ FALSE,
        L0_q117_fever_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      # emesis
      mutate(symptom15dys_vomit_clean = case_when(
        L0_q137_vomit_now_15days == "Yes" ~ TRUE,
        L0_q137_vomit_now_15days == "No" ~ FALSE,
        L0_q137_vomit_now_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) %>%

      # headache
      mutate(symptom15dys_headache_clean = case_when(
        L0_q236_headache_15days == "Yes" ~ TRUE,
        L0_q236_headache_15days == "No" ~ FALSE,
        L0_q236_headache_15days == "." ~ NA,
        TRUE ~ NA
      ) %>% as.factor()) -> cohort_2020_anthro_
      
    cohort_2020_anthro_ %>%
      filter(!deleted) %>%
      filter(L0_q813_who_are_you_following_up_with_individual_id != ".") %>%
      filter(L0_q38_date_followup != ".") %>%
      mutate(uuid_clean = str_c(
        L0_q813_who_are_you_following_up_with_individual_id, 
        L0_q856_unique_id_if_unable_to_select_from_dropdown_above, 
        sep = "_")) %>%
      filter(uuid_clean != "._") %>%
      rowwise() %>%
      mutate(uuid_clean = generate_uid(salt=Sys.getenv("UUID_SALT"), uuid_clean)) %>%
      ungroup() %>%
      group_by(uuid_clean) %>%
      arrange(uuid_clean, date_clean) %>%
      mutate(followup_number_clean = row_number()) %>%
      ungroup() %>%
      mutate(across(contains("diag_"), ~ case_when(
        . == "." ~ NA,
        is.na(.) ~ NA,
        TRUE ~ TRUE
      ) %>% as.factor())) %>%
      rename(village_clean = L0_q791_enumerator) %>%
      select(contains('clean')) %>%
      select(-contains("L0")) %>%
      select(uuid_clean, followup_number_clean, date_clean, village_clean, everything())
}
```
  
```{r example-preprocess_rdp_health_subset2020}
preprocess_rdp_health_subset2020(dharma2020, dharma2019$`Data Dictionary`) %>%
  skim()
```
  
```{r tests-preprocess_rdp_health_subset2020}
test_that("preprocess_rdp_health_subset2020 works", {
  expect_true(inherits(preprocess_rdp_health_subset2020, "function")) 
})
```
  

# preprocess_2019_health

* This function should output month-individuals as rows, where each unit of
measure constitutes one person's month's data.

* For rolling up the clinic to cohort data, we can roll up the
symptoms to ICD10 codes, but preserve the original translations in table.

* see: https://docs.google.com/presentation/d/10ftfDtWDckiPdgOmpoFd9Y2X1cfeLvuT9zPdMZKbmNI/


```{r development-preprocess_2019_health}
# Prepare the code of your function here
```

```{r function-preprocess_2019_health}
#' preprocess_2019_health Title
#'
#' @return 1
#' @export
#'
#' @examples
preprocess_2019_health <- function() {
  1
}
```

```{r examples-preprocess_2019_health}
preprocess_2019_health()
```

```{r tests-preprocess_2019_health}
test_that("preprocess_2019_health works", {
  expect_true(inherits(preprocess_2019_health, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_preprocess_2019_health.Rmd", vignette_name = "Preprocessing 2019 Health Status", check = FALSE, open_vignette = FALSE)
```

