---
title: "flat_dharma_cohort_2019_preprocessing.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this notebook, we will create a template for functions that can be used to preprocess the dharma cohort 2019 data.
The goal is to have a consistent way to preprocess the data, which can then be used in the pipeline.
The functions in this notebook will be used to create a consistent interface for preprocessing the data
to the GoogleDrive folder.

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

First, let's explore the dataset to see what we have and what we need to preprocess.

```{r setup}
pkgload::load_all(export_all = FALSE)
```

# dharma_cohort_2019_preprocessing

```{r development-dharma_cohort_2019_preprocessing}
# Prepare the code of your function here
```

```{r function-dharma_cohort_2019_preprocessing}
#' dharma_cohort_2019_preprocessing Title
#'
#' @return 1
#' @export
#'
#' @examples
dharma_cohort_2019_preprocessing <- function() {
  1
}
```

```{r examples-dharma_cohort_2019_preprocessing}
dharma_cohort_2019_preprocessing()
```

```{r tests-dharma_cohort_2019_preprocessing}
test_that("dharma_cohort_2019_preprocessing works", {
  expect_true(inherits(dharma_cohort_2019_preprocessing, "function"))
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_dharma_cohort_2019_preprocessing.Rmd", vignette_name = "Go further")
```

